Local Spectral Clustering of Density Upper Level Sets

### 2021-09-10 arxiv/appendix.tex

\paragraph{Proof of Lemma~\ref{lem:zhu}.}
As mentioned in the main text, Lemma~\ref{lem:zhu} is equivalent, up to constants, to Lemma~3.4 in \cite{zhu2013}, and the proof of Lemma~\ref{lem:zhu} proceeds along very similar lines to the proof of that lemma. In fact, we directly use the following three inequalities, derived in that work:
\begin{itemize}
	\item \textbf{(c.f. Lemma 3.2 of \cite{zhu2013})} For any seed node $v \in C$, the PPR vector is lower bounded,
	\begin{equation}
	\label{pf:zhu1}
	\wt{p}_v(u) \geq \frac{3}{4}\bigl(1 - \alpha \cdot \tau_{\infty}(\wt{G})\bigr) \cdot \wt{\pi}(u),~~\textrm{for every $u \in C$.}
	\end{equation}
	\item \textbf{(c.f. Corollary 3.3 of \cite{zhu2013})} For any seed node $v \in C$, there exists a so-called leakage distribution $\ell = \ell(v)$ such that $\mathrm{supp}(\ell) \subseteq C$, $\|\ell\|_1 \leq 2\Phi(C;G)/\alpha$, and 
	\begin{equation}
	\label{pf:zhu2}
	p_v(u) \geq \wt{p}_v(u) - \wt{p}_{\ell}(u),~~\textrm{for every $u \in C$.}
	\end{equation}
	\item \textbf{(c.f. Lemma 3.1 of \cite{zhu2013})} There exists a set $C^g \subset C$ with $\vol(C^g;G) \geq \frac{1}{2}\vol(C;G)$ such that for any seed node $v \in C^g$, the following inequality holds
	\begin{equation}
	\label{pf:zhu3}
	p_v(C^c) \leq 2\frac{\Phi(C;G)}{\alpha}.
	\end{equation}
\end{itemize}
teWe use~\eqref{pf:zhu1}-\eqref{pf:zhu3} to separately upper bound $\vol(S_{\beta,v} \setminus C;G)$, $\vol(C^{\mathrm{int}} \setminus S_{\beta,v};G)$ and $\vol(C^{\mathrm{bdry}} \setminus S_{\beta,v};G)$; here $C^{\mathrm{int}} \cup C^{\mathrm{bdry}} = C$ is a partition of $C$, with
\begin{equation*}
C^{\mathrm{int}} := \Bigl\{u \in C: \deg(u;\wt{G}) > \bigl(1 - \alpha \cdot \beta \cdot \vol(C;G)\bigr) \deg(u;G) \Bigr\},
\end{equation*}
consisting of those vertices $u \in C$ with sufficient large degree in $\wt{G}$.

@@

	\textbf{Case 1.}
	Assume $k_j - \Psi(G) \wb{k}_j$ and $k_j + 2 \Psi(G) \wb{k}_j$ are both in $[K_0,2m  - K_0]$. We are therefore in a position to apply our inductive hypothesis to both terms on the right hand side of~\eqref{pf:mixing_random_walk_inductive_step_h} and obtain the following:
	\begin{align*}
	h^{(t)}(k_j) & \leq \frac{1}{2}\biggl(L_{K_0}\bigl(k_j - \Psi(G) \wb{k}_j; h^{(t_0)}\bigr) + L_{K_0}\bigl(k_j + \Psi(G) \wb{k}_j; h^{(t_0)}\bigr) \biggr) ~~+ \\
	& \quad~ \frac{1}{2}C\bigl(K_0; h^{(t_0)}\bigr) \cdot \Bigl(\sqrt{\wb{k_j - \Psi(G) \wb{k}_j}} + \sqrt{\wb{k_j + \Psi(G) \wb{k}_j}}\Bigr)\left(1 - \frac{\Psi(G)^2}{8}\right)^{t-t_0 - 1} \\
	& = L_{K_0}(k;h^{(t_0)}) + \frac{1}{2}\biggl(C(K_0;h^{t_0})\bigl(\sqrt{\wb{k_j - \Psi(G) \wb{k}_j}} + \sqrt{\wb{k_j + \Psi(G) \wb{k}_j}}\bigr)\left(1 - \frac{\Psi(G)^2}{8}\right)^{t-t_0 - 1} \biggr) \\
	& \leq L_{K_0}(k;h^{(t_0)}) + \frac{1}{2}\biggl(C(K_0;h^{(t_0)})\bigl(\sqrt{\wb{k}_j - \Psi(G) \wb{k}_j} + \sqrt{\wb{k}_j + \Psi(G) \wb{k}_j}\bigr)\left(1 - \frac{\Psi(G)^2}{8}\right)^{t-t_0 - 1} \biggr).
	\end{align*}
	A Taylor expansion of $\sqrt{1 + \Psi(G)}$ around $\Psi(G) = 0$ yields the following bound:
	\begin{equation*}
	\sqrt{1 + \Psi(G)} + \sqrt{1 - \Psi(G)} \leq 2 - \frac{\Psi(G)^2}{4},
	\end{equation*}
	and therefore
	\begin{align*}
	h^{(t)}(k_j) & \leq L_{K_0}(k;h^{(t_0)}) + \frac{C(K_0;h^{(t_0)})}{2}\cdot \sqrt{\wb{k}_j}\cdot\left(2 - \frac{\Psi(G)^2}{4}\right)\left(1 - \frac{\Psi(G)^2}{8}\right)^{t-1} \\
	&= L_{K_0}(k_j;h^{(t_0)}) + C(K_0;h^{(t_0)})\sqrt{\wb{k}_j}\left(1 - \frac{\Psi(G)^2}{8}\right)^{t - t_0}.
	\end{align*}

	\textbf{Case 2.} Otherwise one of $k_j - 2 \Psi(G) \wb{k}_j$ or $k_j + 2 \Psi(G) \wb{k}_j$ is not in $[K_0,2m  - K_0]$. Without loss of generality assume $k_j < m$, so that (i) we have $k_j - 2 \Psi(G) \wb{k}_j < K_0$ and (ii) $k_j + (k_j - K_0) \leq 2m - K_0$. We deduce the following:
	\begin{align*}
	h^{(t)}(k_j) & \overset{(\textrm{i})}{\leq} \frac{1}{2}\Bigl(h^{(t - 1)}(K_0) + h^{(t - 1)}\bigl(k_j + (k_j - K_0)\bigr)\Bigr) \\
	& \overset{(\textrm{ii})}{\leq} \frac{1}{2}\Bigl(h^{(t_0)}(K_0) + h^{(t)}\bigl(k_j + (k_j - K_0)\bigr)\Bigr) \\
	& \overset{(\textrm{iii})}{\leq}\frac{1}{2}\Bigl(L_{K_0}(K_0;h^{(t_0)}) + L_{K_0}(2k_j - K_0; h^{(t_0)}\bigr) + C(K_0;h^{(t_0)})\sqrt{\wb{2k_j - K_0}}\left(1 - \frac{\Psi(G)^2}{8}\right)^{t - t_0 - 1}\Bigr) \\
	& \leq L_{K_0}(k_j; h^{(t_0)}) + C(K_0;h^{(t_0)}) \frac{\sqrt{2\wb{k}_j}}{2} \left(1 - \frac{\Psi(G)^2}{8}\right)^{t - t_0 - 1} \\
	& \leq L_{K_0}(k_j;h^{(t_0)}) + C(K_0;h^{(t_0)}) \sqrt{\wb{k}_j} \cdot \left(1 - \frac{\Psi(G)^2}{8}\right)^{t - t_0}
	\end{align*}
	where $(\textrm{(i)})$ follows from~\eqref{pf:mixing_random_walk_inductive_step_h} and the concavity of $h^{(t - 1)}$,  we deduce $(\textrm{ii})$ from~\eqref{pf:mixing_random_walk_inductive_step_h}, which implies that $h^{(t)}(k) \leq h^{(t_0)}(k)$, and $(\textrm{iii})$ follows from applying the inductive hypothesis to $h^{(t - 1)}(2k_j - K_0)$.

@@

	\textbf{Case 1.}
	Assume $k_j - 2 \phi \wb{k}_j$ and $k_j + 2 \phi \wb{k}_j$ are both in $[K_0,2m  - K_0]$. We are therefore in a position to apply our inductive hypothesis to \eqref{eqn:mixing_time_PPR_pf1}, yielding
	\begin{align*}
	h^{(\alpha)}(k_j) & \leq \alpha +~~ \\
	& ~~ \alpha(t-1) \frac{1}{2}\biggl(L_{K_0}(k_j - \phi \wb{k}_j) + L_{K_0}(k_j + \phi \wb{k}_j) + C(K_0;h^{(\alpha)})\bigl(\sqrt{\wb{k_j - \phi \wb{k}_j}} + \sqrt{\wb{k_j + \phi \wb{k}_j}}\bigr)\left(1 - \frac{\phi^2}{8}\right)^{t-1} \biggr) \\
	& \leq \alpha t + L_{K_0}(k;h^{(\alpha)}) + \frac{1}{2}\biggl(C(K_0;h^{(\alpha)})\bigl(\sqrt{\wb{k_j - \phi \wb{k}_j}} + \sqrt{\wb{k_j + \phi \wb{k}_j}}\bigr)\left(1 - \frac{\phi^2}{8}\right)^{t-1} \biggr) \\
	& \leq \alpha t + L_{K_0}(k;h^{(\alpha)}) + \frac{1}{2}\biggl(C(K_0;h^{(\alpha)})\bigl(\sqrt{\wb{k}_j - \phi \wb{k}_j} + \sqrt{\wb{k}_j + \phi \wb{k}_j}\bigr)\left(1 - \frac{\phi^2}{8}\right)^{t-1} \biggr).
	\end{align*}
	and therefore
	\begin{align*}
	h^{(\alpha)}(k_j) & \leq  \alpha t + L_{K_0}(k;h^{(\alpha)}) + \frac{C(K_0;h^{(\alpha)})}{2}\cdot \sqrt{\wb{k}_j}\cdot\left(2 - \frac{\phi^2}{4}\right)\left(1 - \frac{\phi^2}{8}\right)^{t-1} \\
	& = \alpha t + L_{K_0}(k;h^{(\alpha)}) + C(K_0;h^{(\alpha)})\sqrt{\wb{k}_j}\left(1 - \frac{\phi^2}{8}\right)^{t}.
	\end{align*}

@@

\paragraph{Putting the pieces together.} 
First, we note that
\begin{equation*}
\Psi_r(\wt{\mbb{P}}) = \Psi_{\wt{\mbb{P}},r}(\mathrm{supp}(\wt{\mbb{P}})) = \Psi_{\Pbb,r}(\mc{C}), ~~\textrm{and}~~\Psi_{r}(\wt{\mbb{P}}_n) = \Psi_{\wt{\mbb{P}}_n, r}(\mathrm{supp}(\wt{\mbb{P}}_n)) = \Psi_{n,r}(\mc{C}[X]),
\end{equation*}
so that we may apply Proposition~\ref{prop:conductance_lb_transportation_distance} to get a lower bound on $\Psi_{n,r}(\mc{C}[X])$ in terms of $\Psi_{\Pbb,r}(\mc{C})$, $\Delta_{\infty}(\wt{\Pbb}, \wt{\Pbb}_n)$, and $d_{\min}(\wt{\Pbb}_{n})$. We now use the bounds we have derived on transportation distance and minimum degree. From the derivations in Section~\ref{subsec:sample_to_population_conductance}, it follows with probability at least $1 - (n + 1)\exp\{-nb_2/16\}$ that,
\begin{equation*}
d_{\min}(\wt{\Pbb}_n) = \frac{1}{\wt{n}} \bigl(d_{\min}(\wt{G}_{n,r}) + 1\bigr) \geq \frac{1}{\sqrt{2}} d_{\min}(\wt{\Pbb}).
\end{equation*}
% Here I replaced a factor of (1 - 1/sqrt{2})^2 by 1/16, for convenience.
On the other hand, taking
\begin{equation*}
b_6 := \frac{1}{2B_6}\Psi_r(\wt{\Pbb}) \cdot (1 - \Psi_r(\wt{\Pbb})) \cdot d_{\min}(\wt{\Pbb})^2,~~\textrm{and}~~ B_1 := B_5 \Bigl(\min\Bigl\{\frac{b_6}{2\Psi_r(\wt{\Pbb})}, b_6, \frac{r}{4(d - 1)} \Bigr\}\Bigr)^{-1},
\end{equation*}
by~\eqref{eqn:ot_distance_1d} (if $d = 1$) or Theorem~\ref{thm:garciatrillos16} (if $d \geq 2$) along with~\eqref{eqn:sample_to_population_conductance_sample_complexity}, we have that
\begin{equation*}
\Delta_{\infty}(\wt{\Pbb},\wt{\Pbb}_n) \leq B_5 \frac{(\log n)^{p_d}}{\min\{n^{1/2},n^{1/d}\}} \leq \min\Bigl\{\frac{b_6}{2\Psi_r(\wt{\Pbb})}, b_6, \frac{r}{4(d - 1)} \Bigr\} \cdot \delta
\end{equation*}
with probability at least $1 - B_2/n$. Therefore by Proposition~\ref{prop:conductance_lb_transportation_distance},
\begin{equation*}
\Psi_r(\wt{\Pbb}_n) \geq \Psi_r(\wt{\Pbb}) \cdot \biggl(1 - \frac{2B_6\Delta_{\infty}(\wt{\Pbb}_n,\wt{\Pbb})}{\bigl(1 - \Psi_r(\wt{\Pbb})\bigr) \cdot \bigl(d_{\min}(\wt{\Pbb}_n)\bigr)^2}\biggr) - \frac{B_6 \Delta_{\infty}(\wt{\Pbb}_n,\wt{\Pbb}_N)}{\bigl(1 - \Psi_r(\wt{\Pbb})\bigr) \cdot \bigl(d_{\min}(\wt{\Pbb}_n)\bigr)^2} \geq \Psi_r(\wt{\Pbb}) (1 - 2\delta)
\end{equation*}
with probability at least $1 - B_2/n - (n + 1)\exp\{-nb_2/16\}$, establishing~\eqref{eqn:sample_to_population_conductance} upon taking $b_3 := b_2/16$.

@@

\subsection{Isoperimetric inequalities}
\label{subsec:isoperimetric_inequalities}
\citet{dyer1991} establish the following isoperimetric inequality for convex sets.
\begin{lemma}[Isoperimetry of a convex set.]
	\label{lem:convex_isoperimetric_inequality}
	For any partition $(\mc{R}_1,\mc{R}_2,\mc{R}_3)$ of a convex set $\mc{K} \subseteq \Rd$, it holds that
	\begin{equation*}
	\nu(\Omega_3) \geq 2\frac{\mathrm{dist}(\mc{R}_1, \mc{R}_2)}{\mathrm{diam}(\mc{K})} \min(\nu(\mc{R}_1), \nu(\mc{R}_2)).
	\end{equation*}
\end{lemma}
\citet{abbasi-yadkori2016a} points out that if $\mc{S}$ is the image of a convex set under a Lipschitz measure-preserving mapping $g: \Rd \to \Rd$, a similar inequality can be obtained.
\begin{corollary}[Isoperimetry of Lipschitz embeddings of convex sets.]
	\label{cor:nonconvex_isoperimetric_inequality}
	Suppose $\mc{S}$ is the image of a convex set $\mathcal{K}$ under a mapping $g:\Rd \to \Rd$ such that
	\begin{equation*}
	\|g(x) - g(y)\| \leq L \cdot \|x - y\|,~~\textrm{for all $x,y \in \mc{K}$, and}~~\det(\nabla g(x)) = 1~~\textrm{for all $x \in \mc{K}$.}
	\end{equation*}
	Then for any partition $(\Omega_1,\Omega_2,\Omega_3)$ of $\mc{S}$, 
	\begin{equation*}
	\nu(\Omega_3) \geq 2\frac{\mathrm{dist}(\Omega_1, \Omega_2)}{\diam(\mc{K}) L} \min(\nu(\Omega_1), \nu(\Omega_2)).
	\end{equation*}
\end{corollary}

@@

	It remains to verify that $x \mapsto \nu\bigl(\mc{A}_j(s)\bigr)/\nu\bigl(B(x_j,s)\bigr)$ is monotonically non-increasing. For any $0 < s < t$ and $j = 1,\ldots,N$, suppose $x \in \mc{A}_j(T) - \{x_j\}$, meaning $x \in B(0,t)$ and $x \not\in B(x_i - x_j,t)$ for any $i = 1,\ldots,j - 1$. Thus $(s/t)x \in B(0,s)$, and
	\begin{equation*}
	\|(s/t)x - (x_i - x_j)\| \geq \|x - (x_i - x_j)\| - \|x - (s/t)x\| > t - (1 - s/t)\|x\| \geq t - (1 - s/t)t = s,
	\end{equation*}
	or in other words $(s/t)x \not\in B(x_i - x_j,s)$ for any $i = 1,\ldots,j - 1$. Consequently,
	\begin{equation*}
	\Bigl(\mc{A}_j(t) - \{x_j\}\Bigr) \subset \frac{t}{s} \cdot \Bigl(\mc{A}_{j}(s)- \{x_j\}\Bigr),
	\end{equation*}
	and applying $\nu(\cdot)$ to both sides yields the claim.

@@

		and likewise for $\vol_{\wt{\nu},r}(\mc{S})$. Therefore,

>>>>

\paragraph{Proof of Lemma~\ref{lem:zhu}.}
As mentioned in the main text, Lemma~\ref{lem:zhu} is equivalent, up to constants, to Lemma~3.4 in \cite{zhu2013}, and the proof of Lemma~\ref{lem:zhu} proceeds along very similar lines to the proof of that lemma. In fact, we directly use the following three inequalities, derived in that work:
\begin{itemize}
	\item \textbf{(c.f. Lemma 3.2 of \cite{zhu2013})} For any seed node $v \in C$, the PPR vector is lower bounded,
	\begin{equation}
	\label{pf:zhu1}
	\wt{p}_v(u) \geq \frac{3}{4}\bigl(1 - \alpha \cdot \tau_{\infty}(\wt{G})\bigr) \cdot \wt{\pi}(u),~~\textrm{for every $u \in C$.}
	\end{equation}
	\item \textbf{(c.f. Corollary 3.3 of \cite{zhu2013})} For any seed node $v \in C$, there exists a so-called leakage distribution $\ell = \ell(v)$ such that $\mathrm{supp}(\ell) \subseteq C$, $\|\ell\|_1 \leq 2\Phi(C;G)/\alpha$, and 
	\begin{equation}
	\label{pf:zhu2}
	p_v(u) \geq \wt{p}_v(u) - \wt{p}_{\ell}(u),~~\textrm{for every $u \in C$.}
	\end{equation}
	\item \textbf{(c.f. Lemma 3.1 of \cite{zhu2013})} There exists a set $C^g \subset C$ with $\vol(C^g;G) \geq \frac{1}{2}\vol(C;G)$ such that for any seed node $v \in C^g$, the following inequality holds
	\begin{equation}
	\label{pf:zhu3}
	p_v(C^c) \leq 2\frac{\Phi(C;G)}{\alpha}.
	\end{equation}
\end{itemize}
We use~\eqref{pf:zhu1}-\eqref{pf:zhu3} to separately upper bound $\vol(S_{\beta,v} \setminus C;G)$, $\vol(C^{\mathrm{int}} \setminus S_{\beta,v};G)$ and $\vol(C^{\mathrm{bdry}} \setminus S_{\beta,v};G)$; here $C^{\mathrm{int}} \cup C^{\mathrm{bdry}} = C$ is a partition of $C$, with
\begin{equation*}
C^{\mathrm{int}} := \Bigl\{u \in C: \deg(u;\wt{G}) > \bigl(1 - \alpha \cdot \beta \cdot \vol(C;G)\bigr) \deg(u;G) \Bigr\},
\end{equation*}
consisting of those vertices $u \in C$ with sufficient large degree in $\wt{G}$.

@@

	\textbf{Case 1.}
	Assume $k_j - \Psi(G) \wb{k}_j$ and $k_j + 2 \Psi(G) \wb{k}_j$ are both in $[K_0,2m  - K_0]$. We are therefore in a position to apply our inductive hypothesis to both terms on the right hand side of~\eqref{pf:mixing_random_walk_inductive_step_h}, and obtain the following:
	\begin{align*}
	h^{(t)}(k_j) & \leq \frac{1}{2}\biggl(L_{K_0}\bigl(k_j - \Psi(G) \wb{k}_j; h^{(t_0)}\bigr) + L_{K_0}\bigl(k_j + \Psi(G) \wb{k}_j; h^{(t_0)}\bigr) \biggr) ~~+ \\
	& \quad~ \frac{1}{2}C\bigl(K_0; h^{(t_0)}\bigr) \cdot \Bigl(\sqrt{\overline{k_j - \Psi(G) \wb{k}_j}} + \sqrt{\overline{k_j + \Psi(G) \wb{k}_j}}\Bigr)\left(1 - \frac{\Psi(G)^2}{8}\right)^{t-t_0 - 1} \\
	& = L_{K_0}(k;h^{(t_0)}) + \frac{1}{2}\biggl(C(K_0;h^{t_0})\bigl(\sqrt{\overline{k_j - \Psi(G) \wb{k}_j}} + \sqrt{\overline{k_j + \Psi(G) \wb{k}_j}}\bigr)\left(1 - \frac{\Psi(G)^2}{8}\right)^{t-t_0 - 1} \biggr) \\
	& \leq L_{K_0}(k;h^{(t_0)}) + \frac{1}{2}\biggl(C(K_0;h^{(t_0)})\bigl(\sqrt{\wb{k}_j - \Psi(G) \wb{k}_j} + \sqrt{\wb{k}_j + \Psi(G) \wb{k}_j}\bigr)\left(1 - \frac{\Psi(G)^2}{8}\right)^{t-t_0 - 1} \biggr).
	\end{align*}
	A Taylor expansion of $\sqrt{1 + \Psi(G)}$ around $\Psi(G) = 0$ yields the following bound:
	\begin{equation*}
	\sqrt{1 + \Psi(G)} + \sqrt{1 - \Psi(G)} \leq 2 - \frac{\Psi(G)^2}{4},
	\end{equation*}
	and therefore
	\begin{align*}
	h^{(t)}(k_j) & \leq L_{K_0}(k;h^{(t_0)}) + \frac{C(K_0;h^{(t_0)})}{2}\cdot \sqrt{\wb{k}_j}\cdot\left(2 - \frac{\Psi(G)^2}{4}\right)\left(1 - \frac{\Psi(G)^2}{8}\right)^{t-1} \\
	&= L_{K_0}(k_j;h^{(t_0)}) + C(K_0;h^{(t_0)})\sqrt{\wb{k}_j}\left(1 - \frac{\Psi(G)^2}{8}\right)^{t - t_0}.
	\end{align*}

	\textbf{Case 2.} Otherwise one of $k_j - 2 \Psi(G) \wb{k}_j$ or $k_j + 2 \Psi(G) \wb{k}_j$ is not in $[K_0,2m  - K_0]$. Without loss of generality assume $k_j < m$, so that (i) we have $k_j - 2 \Psi(G) \wb{k}_j < K_0$ and (ii) $k_j + (k_j - K_0) \leq 2m - K_0$. We deduce the following:
	\begin{align*}
	h^{(t)}(k_j) & \overset{(\textrm{i})}{\leq} \frac{1}{2}\Bigl(h^{(t - 1)}(K_0) + h^{(t - 1)}\bigl(k_j + (k_j - K_0)\bigr)\Bigr) \\
	& \overset{(\textrm{ii})}{\leq} \frac{1}{2}\Bigl(h^{(t_0)}(K_0) + h^{(t)}\bigl(k_j + (k_j - K_0)\bigr)\Bigr) \\
	& \overset{(\textrm{iii})}{\leq}\frac{1}{2}\Bigl(L_{K_0}(K_0;h^{(t_0)}) + L_{K_0}(2k_j - K_0; h^{(t_0)}\bigr) + C(K_0;h^{(t_0)})\sqrt{\overline{2k_j - K_0}}\left(1 - \frac{\Psi(G)^2}{8}\right)^{t - t_0 - 1}\Bigr) \\
	& \leq L_{K_0}(k_j; h^{(t_0)}) + C(K_0;h^{(t_0)}) \frac{\sqrt{2\wb{k}_j}}{2} \left(1 - \frac{\Psi(G)^2}{8}\right)^{t - t_0 - 1} \\
	& \leq L_{K_0}(k_j;h^{(t_0)}) + C(K_0;h^{(t_0)}) \sqrt{\wb{k}_j} \cdot \left(1 - \frac{\Psi(G)^2}{8}\right)^{t - t_0}
	\end{align*}
	where $(\textrm{(i)})$ follows from~\eqref{pf:mixing_random_walk_inductive_step_h} and the concavity of $h^{(t - 1)}$,  we deduce $(\textrm{ii})$ from~\eqref{pf:mixing_random_walk_inductive_step_h}, which implies that $h^{(t)}(k) \leq h^{(t_0)}(k)$, and $(\textrm{iii})$ follows from applying the inductive hypothesis to $h^{(t - 1)}(2k_j - K_0)$.

@@

	\textbf{Case 1.}
	Assume $k_j - 2 \phi \wb{k}_j$ and $k_j + 2 \phi \wb{k}_j$ are both in $[K_0,2m  - K_0]$. We are therefore in a position to apply our inductive hypothesis to \eqref{eqn:mixing_time_PPR_pf1}, yielding
	\begin{align*}
	h^{(\alpha)}(k_j) & \leq \alpha +~~ \\
	& ~~ \alpha(t-1) \frac{1}{2}\biggl(L_{K_0}(k_j - \phi \wb{k}_j) + L_{K_0}(k_j + \phi \wb{k}_j) + C(K_0;h^{(\alpha)})\bigl(\sqrt{\overline{k_j - \phi \wb{k}_j}} + \sqrt{\overline{k_j + \phi \wb{k}_j}}\bigr)\left(1 - \frac{\phi^2}{8}\right)^{t-1} \biggr) \\
	& \leq \alpha t + L_{K_0}(k;h^{(\alpha)}) + \frac{1}{2}\biggl(C(K_0;h^{(\alpha)})\bigl(\sqrt{\overline{k_j - \phi \wb{k}_j}} + \sqrt{\overline{k_j + \phi \wb{k}_j}}\bigr)\left(1 - \frac{\phi^2}{8}\right)^{t-1} \biggr) \\
	& \leq \alpha t + L_{K_0}(k;h^{(\alpha)}) + \frac{1}{2}\biggl(C(K_0;h^{(\alpha)})\bigl(\sqrt{\wb{k}_j - \phi \wb{k}_j} + \sqrt{\wb{k}_j + \phi \wb{k}_j}\bigr)\left(1 - \frac{\phi^2}{8}\right)^{t-1} \biggr).
	\end{align*}
	and therefore
	\begin{align*}
	h^{(\alpha)}(k_j) & \leq  \alpha t + L_{K_0}(k;h^{(\alpha)}) + \frac{C(K_0;h^{(\alpha)})}{2}\cdot \sqrt{\wb{k}_j}\cdot\left(2 - \frac{\phi^2}{4}\right)\left(1 - \frac{\phi^2}{8}\right)^{t-1} \\
	& = \alpha t + L_{K_0}(k;h^{(\alpha)}) + C(K_0;h^{(\alpha)})\sqrt{\wb{k}_j}\left(1 - \frac{\phi^2}{8}\right)^{t}.
	\end{align*}

@@

\paragraph{Putting the pieces together.} 
First, we note that
\begin{equation*}
\Psi_r(\wt{\mbb{P}}) = \Psi_{\wt{\mbb{P}},r}(\mathrm{supp}(\wt{\mbb{P}})) = \Psi_{\Pbb,r}(\mc{C}), ~~\textrm{and}~~\Psi_{r}(\wt{\mbb{P}}_n) = \Psi_{\wt{\mbb{P}}_n, r}(\mathrm{supp}(\wt{\mbb{P}}_n)) = \Psi_{n,r}(\mc{C}[X]),
\end{equation*}
so that we may apply Proposition~\ref{prop:conductance_lb_transportation_distance} to get a lower bound on $\Psi_{n,r}(\mc{C}[X])$ in terms of $\Psi_{\Pbb,r}(\mc{C})$, $\Delta_{\infty}(\wt{\Pbb}, \wt{\Pbb}_n)$, and $d_{\min}(\wt{\Pbb}_{n})$. We now use the bounds we have derived on transportation distance and minimum degree. From the derivations in Section~\ref{subsec:sample_to_population_conductance}, it follows with probability at least $1 - (n + 1)\exp\{-nb_2/16\}$ that,
\begin{equation*}
d_{\min}(\wt{\Pbb}_n) = \frac{1}{\wt{n}} \bigl(d_{\min}(\wt{G}_{n,r}) + 1\bigr) \geq \frac{1}{\sqrt{2}} d_{\min}(\wt{\Pbb}).
\end{equation*}
% Here I replaced a factor of (1 - 1/sqrt{2})^2 by 1/16, for convenience.
On the other hand, taking
\begin{equation*}
b_6 := \frac{1}{2B_6}\Psi_r(\wt{\Pbb}) \cdot (1 - \Psi_r(\wt{\Pbb})) \cdot d_{\min}(\wt{\Pbb})^2,~~\textrm{and}~~ B_1 := B_5 \Bigl(\min\Bigl\{\frac{b_6}{2\Psi_r(\wt{\Pbb})}, b_6, \frac{r}{4(d - 1)} \Bigr\}\Bigr)^{-1},
\end{equation*}
by~\eqref{eqn:ot_distance_1d} (if $d = 1$) or Theorem~\ref{thm:garciatrillos16} (if $d \geq 2$) along with~\eqref{eqn:sample_to_population_conductance_sample_complexity}, we have that
\begin{equation*}
\Delta_{\infty}(\wt{\Pbb},\wt{\Pbb}_n) \leq B_5 \frac{(\log n)^{p_d}}{\min\{n^{1/2},n^{1/d}\}} \leq \min\Bigl\{\frac{b_6}{2\Psi_r(\wt{\Pbb})}, b_6, \frac{r}{4(d - 1)} \Bigr\} \cdot \delta
\end{equation*}
with probability at least $1 - B_2/n$. Therefore by Proposition~\ref{prop:conductance_lb_transportation_distance},
\begin{equation*}
\Psi_r(\wt{\Pbb}_n) \geq \Psi_r(\wt{\Pbb}) \cdot \biggl(1 - \frac{2B_6\Delta_{\infty}(\wt{\Pbb}_n,\wt{\Pbb})}{\bigl(1 - \Psi_r(\wt{\Pbb})\bigr) \cdot \bigl(d_{\min}(\wt{\Pbb}_n)\bigr)^2}\biggr) - \frac{B_6 \Delta_{\infty}(\wt{\Pbb}_n,\wt{\Pbb})}{\bigl(1 - \Psi_r(\wt{\Pbb})\bigr) \cdot \bigl(d_{\min}(\wt{\Pbb}_n)\bigr)^2} \geq \Psi_r(\wt{\Pbb}) (1 - 2\delta)
\end{equation*}
with probability at least $1 - B_2/n - (n + 1)\exp\{-nb_2/16\}$, establishing~\eqref{eqn:sample_to_population_conductance} upon taking $b_3 := b_2/16$.

@@

\subsection{Isoperimetric inequalities}
\label{subsec:isoperimetric_inequalities}
\citet{dyer1991} establish the following isoperimetric inequality for convex sets.
\begin{lemma}[Isoperimetry of a convex set.]
	\label{lem:convex_isoperimetric_inequality}
	For any partition $(\mc{R}_1,\mc{R}_2,\mc{R}_3)$ of a convex set $\mc{K} \subseteq \Rd$, it holds that
	\begin{equation*}
	\nu(\mc{R}_3) \geq 2\frac{\mathrm{dist}(\mc{R}_1, \mc{R}_2)}{\mathrm{diam}(\mc{K})} \min(\nu(\mc{R}_1), \nu(\mc{R}_2)).
	\end{equation*}
\end{lemma}
\citet{abbasi-yadkori2016a} points out that if $\mc{S}$ is the image of a convex set under a Lipschitz measure-preserving mapping $g: \Rd \to \Rd$, a similar inequality can be obtained.
\begin{corollary}[Isoperimetry of Lipschitz embeddings of convex sets.]
	\label{cor:nonconvex_isoperimetric_inequality}
	Suppose $\mc{S}$ is the image of a convex set $\mathcal{K}$ under a mapping $g:\Rd \to \Rd$ such that
	\begin{equation*}
	\|g(x) - g(y)\| \leq L \cdot \|x - y\|,~~\textrm{for all $x,y \in \mc{K}$, and}~~\det(\nabla g(x)) = 1~~\textrm{for all $x \in \mc{K}$.}
	\end{equation*}
	Then for any partition $(\Omega_1,\Omega_2,\Omega_3)$ of $\mc{S}$, 
	\begin{equation*}
	\nu(\Omega_3) \geq 2\frac{\mathrm{dist}(\Omega_1, \Omega_2)}{\diam(\mc{K}) L} \min(\nu(\Omega_1), \nu(\Omega_2)).
	\end{equation*}
\end{corollary}

@@

	It remains to verify that $s \mapsto \nu\bigl(\mc{A}_j(s)\bigr)/\nu\bigl(B(x_j,s)\bigr)$ is monotonically non-increasing. For any $0 < s < t$ and $j = 1,\ldots,N$, suppose $x \in \mc{A}_j(T) - \{x_j\}$, meaning $x \in B(0,t)$ and $x \not\in B(x_i - x_j,t)$ for any $i = 1,\ldots,j - 1$. Thus $(s/t)x \in B(0,s)$, and
	\begin{equation*}
	\|(s/t)x - (x_i - x_j)\| \geq \|x - (x_i - x_j)\| - \|x - (s/t)x\| > t - (1 - s/t)\|x\| \geq t - (1 - s/t)t = s,
	\end{equation*}
	or in other words $(s/t)x \not\in B(x_i - x_j,s)$ for any $i = 1,\ldots,j - 1$. Consequently,
	\begin{equation*}
	\Bigl(\mc{A}_j(t) - \{x_j\}\Bigr) \subset \frac{t}{s} \cdot \Bigl(\mc{A}_{j}(s)- \{x_j\}\Bigr),
	\end{equation*}
	and applying $\nu(\cdot)$ to both sides yields the claim.

@@

		and likewise for $\vol_{\wt{\nu},r}(\mc{R})$. Therefore,
